\plaintitle

### 2017-06-07 papers/IoT2017/related.tex

\section{Related Work}
\label{sec:related}

\subsection{Smart Grid and Meter Privacy}

% http://ieeexplore.ieee.org/abstract/document/5054916/
%McDaniel and McLaughlin discuss privacy challenges in smart grids~\cite{mcdaniel2009security}.

% https://arxiv.org/pdf/1108.2234.pdf
% https://pdfs.semanticscholar.org/cdf8/a5b6256823bca38a1d2347ab36f8e4a2ca94.pdf

% http://www.comm.toronto.edu/~akhisti/sm.pdf

% https://www.researchgate.net/profile/Georgios_Kalogridis/publication/224189766_Smart_Grid_Privacy_via_Anonymization_of_Smart_Metering_Data/links/541169510cf2b4da1bec4193.pdf

% https://arxiv.org/pdf/1305.0735.pdf
New privacy concerns arise with the continuing adoption of smart grids. In addition to both old and new security threats, such as energy theft and smart meter malware, McDaniel and McLaughlin discuss the privacy concerns of energy usage profiling that smart grids could potentially enable~\cite{mcdaniel2009security}. Several approaches have been investigated as potential means to provide privacy protections for smart grid users.

@@

\subsection{Blockchain Technology}

As Blockchain technology continues to develop and mature, new frameworks, services, and protocols are being developed to leverage blockchain's distributed ledger. Microsoft offers Blockchain as a Service (BaaS) on Azure. Additionally, Microsoft has Project Bletchley as its architectural approach to building an Enterprise Consortium Blockchain Ecosystem, introducing two new concepts: blockchain middleware and a secure means for calling code or data outside a SmartContract or blockchain called cryptlets~\cite{gray2016introducing}. Hyperledger Fabric is a platform for distributed ledger solutions, which was designed to support pluggable implementations of different components~\cite{hyperledger2017fabric}. Bitcoin Lightning Network is decentralized system, in which transactions are sent over a network of micropayment channels whose transfer of value occurs off-blockchain~\cite{poon2016bitcoin}. Interledger is a protocol for payments across payment systems, which enables anyone with accounts on two ledgers to create
a connection between them~\cite{thomas_protocol}. Xu et al.\ discuss the use of two pools of proxy agents, an agreement pool and a payment pool, to assist in protection of privacy when using blockchain technologies for transactions on tangible goods~\cite{Xu2017}.

>>>>

%!TEX root = paper.tex
\section{Related Work}
\label{sec:related}

%In this section we describe the related research. It has been divided into two subsections to focus on blockchains, which we are using to implement the distributed ledger service described earlier, and other works on smart grid privacy concerns.

%\subsection{Smart Grid and Meter Privacy}
% http://ieeexplore.ieee.org/abstract/document/5054916/
%McDaniel and McLaughlin discuss privacy challenges in smart grids~\cite{mcdaniel2009security}.
% https://arxiv.org/pdf/1108.2234.pdf
% https://pdfs.semanticscholar.org/cdf8/a5b6256823bca38a1d2347ab36f8e4a2ca94.pdf
% http://www.comm.toronto.edu/~akhisti/sm.pdf
% https://www.researchgate.net/profile/Georgios_Kalogridis/publication/224189766_Smart_Grid_Privacy_via_Anonymization_of_Smart_Metering_Data/links/541169510cf2b4da1bec4193.pdf
% https://arxiv.org/pdf/1305.0735.pdf
New privacy concerns arise with the continuing adoption of smart grids. In addition to both old and new security threats, such as energy theft and smart meter malware, McDaniel and McLaughlin discuss the privacy concerns of energy usage profiling that smart grids could potentially enable~\cite{mcdaniel2009security}. Several approaches have been investigated as potential means to provide privacy protections for smart grid users.

@@

Our solution extends earlier work by considering a decentralized IoT system for transactive energy, and addressing the novel privacy threat posed by trading. In other words, while earlier results protected prosumers' privacy from the DSO, we protect privacy from other prosumers as well as from outside attackers.

A key element of our approach is the ability to distribute the informtion among peers. For that purpose, we rely on the use of Blockchains. 
As Blockchain technology continues to develop and mature, new frameworks, services, and protocols are being developed to leverage blockchain's distributed ledger. Hyperledger Fabric is a platform for distributed ledger solutions, which was designed to support pluggable implementations of different components~\cite{hyperledger2017fabric}. Bitcoin Lightning Network is decentralized system, in which transactions are sent over a network of micropayment channels whose transfer of value occurs off-blockchain~\cite{poon2016bitcoin}. However, this paper focuses on theoretical aspects of our implementation and as such any one of these distributed ledgers provide the required capabilities.\Abhishek{Aron please see this paragraph}

%\Abhishek{Aron this section should end with a few sentence about how our approach fits in. Perhaps just a few sentences reworded from introduction will be sufficient}

\iffalse
\subsection{Blockchains as Distributed Ledgers}

As Blockchain technology continues to develop and mature, new frameworks, services, and protocols are being developed to leverage blockchain's distributed ledger. Microsoft offers Blockchain as a Service (BaaS) on Azure. Additionally, Microsoft has Project Bletchley as its architectural approach to building an Enterprise Consortium Blockchain Ecosystem, introducing two new concepts: blockchain middleware and a secure means for calling code or data outside a SmartContract or blockchain called cryptlets~\cite{gray2016introducing}. Hyperledger Fabric is a platform for distributed ledger solutions, which was designed to support pluggable implementations of different components~\cite{hyperledger2017fabric}. Bitcoin Lightning Network is decentralized system, in which transactions are sent over a network of micropayment channels whose transfer of value occurs off-blockchain~\cite{poon2016bitcoin}. Interledger is a protocol for payments across payment systems, which enables anyone with accounts on two ledgers to create
a connection between them~\cite{thomas_protocol}. Xu et al.\ discuss the use of two pools of proxy agents, an agreement pool and a payment pool, to assist in protection of privacy when using blockchain technologies for transactions on tangible goods~\cite{Xu2017}.
\fi
